Toward Centrally Programming Distributed Control Planes

### 2016-01-23 paper/expressiveness.tex
Cleaning up bullet points, starting expressiveness.

@@

\para{Expressiveness}

In this section, we compare the expressiveness of the \sysname language to that of BGP.

\todo{Do we need all of this}

>>>>

\subsection{Expressiveness}

Models for BGP are traditionally given over per-device ranked paths 
In this section, we describe the expressiveness of \sysname.

\begin{defn}

\end{defn}

@@

An important distinction is that BGP might still be instable with respect to other external ASes, since \sysname has no way of configuring their routing policy and can only rely on AS path filters to see what advertisements are observed.
